\newgeometry{tmargin=25mm, lmargin=38mm, rmargin=25mm, bmargin=25mm}
%\vspace{1.26 cm}
%\vspace{-6.0\baselineskip}
%\vspace{5cm}
\textbf{\begin{flushright}
		{\LARGE \textbf{Acknowledgements}}
\end{flushright}}
\vspace{-0.8\baselineskip}
\noindent\rule{\linewidth}{2pt}

\par Inscribing these words of gratitude feels akin to painting a masterpiece on the canvas of appreciation. This incredible path of learning and exploration would not have been possible without the unflinching support and encouragement of the great individuals who have paved the road for our accomplishment. \\
\par We reserve a special place in my heart for our beloved parents, whose unwavering love, unwavering support, and unwavering belief in our abilities have been the bedrock upon which my dreams have flourished. Their persistent support, sacrifices, and unshakable trust in our abilities have been the driving factors behind our quest for knowledge and academic pursuits.\\
\par First and foremost, We owe a tremendous debt of gratitude to my esteemed supervisor, \textbf{Dr. Asit Kumar Das}, whose guidance and advice have been the compass guiding us through the many twists and turns of this thesis. His stimulating conversations, insightful feedback, kind advice, and boundless forbearance have challenged us to push the boundaries of our capabilities and inspired us to strive for academic excellence. We are very thankful for the trust you put in us and the chances you gave us to grow both professionally and personally. We are grateful beyond words for the opportunity to have worked under your guidance, and we hope my thesis serves as a fitting tribute to your hard work, knowledge, and encouragement.\\
\par We like to thank \textbf{Dr. Chayan Halder}, Assistant Professor, Department of Computer Science, Ramakrishna Mission Vivekananda Centenary College for his extended support. Without his continuous support and help, this project would be impossible to finish properly.\\
\par We would like to extend a heartfelt thank you to our incredible classmates and friends, who have been a constant source of support, camaraderie, and inspiration. Their presence has made the often-trying process of writing a thesis into one that is filled with joy and fun. Finally, We want to thank everyone who helped me grow as a scholar and made this trip unforgettable.\\
\begin{flushright}
 \hfill \textbf{ Jishnu Bandyopadhyay}
\end{flushright}
\vspace{0.3cm}
\begin{flushright}
	\hfill \textbf{ Bitan Majumder}
\end{flushright}