%\chapter*{References} \label{references} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\noindent\rule{\linewidth}{2pt}
%\renewcommand{\bibname}{References}

\begin{thebibliography}{00}
\bibitem{b1} Rosell, Fred A., et al. The Fundamentals of Thermal Imaging Systems. Naval Research Lab Washington DC, 1979.
\bibitem{b2} Planinsic, Gorazd. ``Infrared thermal imaging: fundamentals, research and applications." (2011): 1431.
\bibitem{b3} Vollmer, Michael. ``Infrared thermal imaging." Computer Vision: A Reference Guide. Cham: Springer International Publishing, 2021. 666-670.
\bibitem{b4} Gade, Rikke, and Thomas B. Moeslund. ``Thermal cameras and applications: a survey." Machine vision and applications 25 (2014): 245-262.
\bibitem{b5} Sosnowski, Tomasz, Grzegorz Bieszczad, and Henryk Madura. ``Image processing in thermal cameras." Advanced technologies in practical applications for national security (2018): 35-57.
\bibitem{b6} Dey, Nilanjan, Amira S. Ashour, and Afnan S. Althoupety. ``Thermal imaging in medical science." Recent Advances in Applied Thermal Imaging for Industrial Applications (2017): 87-117.
\bibitem{b7} Jiang, L. J., et al. ``A perspective on medical infrared imaging." Journal of medical engineering \& technology 29.6 (2005): 257-267.
\bibitem{b8} Aljumah, Abdullah A., Mohammed Gulam Ahamad, and Mohammad Khubeb Siddiqui. ``Application of data mining: Diabetes health care in young and old patients." Journal of King Saud University-Computer and Information Sciences 25.2 (2013): 127-136.
\bibitem{b9} Al-Nozha, Mansour M et al. ``Diabetes mellitus in Saudi Arabia.” Saudi medical journal vol. 25,11 (2004): 1603-10.
\bibitem{b10} Kaur, Harleen, and Vinita Kumari. ``Predictive modelling and analytics for diabetes using a machine learning approach." Applied computing and informatics 18.1/2 (2022): 90-100.
\bibitem{b11} Maldonado, H., et al. ``Automatic detection of risk zones in diabetic foot soles by processing thermographic images taken in an uncontrolled environment." Infrared Physics \& Technology 105 (2020): 103187.
\bibitem{b12} Swapna, Goutham, Soman Kp, and Ravi Vinayakumar. ``Automated detection of diabetes using CNN and CNN-LSTM network and heart rate signals." Procedia computer science 132 (2018): 1253-1262.
\bibitem{b13} Selvarani, A., and G. R. Suresh. ``Infrared thermal imaging for diabetes detection and measurement." Journal of medical systems 43 (2019): 1-11.
\bibitem{b14} Kayalvizhi, M., and D. Maheswari. ``A Hybrid Deep Learning Algorithms For Diabetes Mellitus Prediction Using Thermal Foot Images." European Journal of Molecular \& Clinical Medicine 7.11 (2021): 5176-5183.
\bibitem{b15} van Netten, Jaap J., et al. ``Infrared thermal imaging for automated detection of diabetic foot complications." Journal of diabetes science and technology 7.5 (2013): 1122-1129.
\bibitem{b16} Filipe, Vítor, Pedro Teixeira, and Ana Teixeira. ``A clustering approach for prediction of diabetic foot using thermal images." Computational Science and Its Applications–ICCSA 2020: 20th International Conference, Cagliari, Italy, July 1–4, 2020, Proceedings, Part III 20. Springer International Publishing, 2020.
\bibitem{b17} Lange, K. H. W., et al. ``Skin temperature measured by infrared thermography after specific ultrasound-guided blocking of the musculocutaneous, radial, ulnar, and median nerves in the upper extremity." British journal of anaesthesia 106.6 (2011): 887-895.
\bibitem{b18} Arora, Ajat Shatru, and Jaspreet Singh. ``Paranasal sinusitis detection using thermal imaging." 2015 Science and Information Conference (SAI). IEEE, 2015.
\bibitem{b19} Ozbay, S., and O. Tunc. ``Deep Learning in Analysing Paranasal Sinuses”. Elektronika Ir Elektrotechnika, vol. 28, no. 3, June 2022, pp. 65-70.
\bibitem{b20} Rustam, Z., et al. ``Acute sinusitis classification using support and fuzzy support vector machines." Journal of Physics: Conference Series. Vol. 1490. No. 1. IOP Publishing, 2020.
\bibitem{b21} Kalaiarasi, Raja, et al. ``Role of thermography in the diagnosis of chronic sinusitis." Cureus 10.3 (2018).
\bibitem{b22} Ring, E. F. J., et al. ``New standards for fever screening with thermal imaging systems." Journal of Mechanics in Medicine and Biology 13.02 (2013): 1350045.
\bibitem{b23} Ordun, Catherine, Edward Raff, and Sanjay Purushotham. ``The use of AI for thermal emotion recognition: A review of problems and limitations in standard design and data." arXiv preprint arXiv:2009.10589 (2020).
\bibitem{b24} A. Basu, A. Routray, S. Shit, and A. K. Deb, ``Human emotion recognition from facial thermal image based on fused statistical feature and multi-class SVM," 2015 Annual IEEE India Conference (INDICON), 2015, pp. 1-5.
\bibitem{b25} Priya, M. S., and GM Kadhar Nawaz. ``Modified emotion recognition system to study the emotion cues through thermal facial analysis." Biomedical Research 28.20, 2017, pp. 8718-8723.
\bibitem{b26} Schaefer, Alexandre, et al. ``Assessing the effectiveness of a large database of emotion-eliciting films: A new tool for emotion researchers." Cognition and emotion 24.7, 2010, pp. 1153-1172.
\bibitem{b27} A. Kolli, A. Fasih, F. A. Machot and K. Kyamakya, "Non-intrusive car driver's emotion recognition using thermal camera," Proceedings of the Joint INDS'11 \& ISTET'11, Klagenfurt am Wörthersee, Austria, 2011, pp. 1-5.
\bibitem{b28} Acheampong, Francisca Adoma, Chen Wenyu, and Henry Nunoo‐Mensah. ``Text‐based emotion detection: Advances, challenges, and opportunities." Engineering Reports 2.7, e12189, Jul. 2020.
\bibitem{b29} Yu, Feng, et al. ``Emotion detection from speech to enrich multimedia content." Pacific-Rim Conference on Multimedia. Springer, Berlin, Heidelberg, Nov. 2001, pp. 550-557.
\bibitem{b30} Koch, Christian, et al. ``A review on computer vision based defect detection and condition assessment of concrete and asphalt civil infrastructure." Advanced Engineering Informatics 29.2 (2015): 196-210.
\bibitem{b31} Mohan, Arun, and Poobal, Sumathi. ``Crack Detection Using Image Processing: A Critical Review and Analysis." Alexandria Engineering Journal, vol. 57, no. 2, 2018, pp. 787-798.
\bibitem{b32} Noh, Yohwan, et al. ``Automatic crack detection on concrete images using segmentation via fuzzy C-means clustering." 2017 International conference on applied system innovation (ICASI). IEEE, 2017.
\bibitem{b33} Dinh, Tran Hiep, Quang Phuc Ha, and Hung M. La. ``Computer vision-based method for concrete crack detection." 2016 14th international conference on control, automation, robotics and vision (ICARCV). IEEE, 2016.
\bibitem{b34} Ali, Rahmat, Dharshan Lokekere Gopal, and Young-Jin Cha. ``Vision-based concrete crack detection technique using cascade features." Sensors and Smart Structures Technologies for Civil, Mechanical, and Aerospace Systems 2018. Vol. 10598. SPIE, 2018.
\bibitem{b35} Adhikari, R. S., O. Moselhi, and A. Bagchi. ``Image-based retrieval of concrete crack properties for bridge inspection." Automation in Construction 39 (2014): 180-194.
\bibitem{b36} Kim, Byunghyun, and Soojin Cho. ``Automated vision-based detection of cracks on concrete surfaces using a deep learning technique." Sensors 18.10 (2018): 3452.
\bibitem{b37} Tong, Zheng, et al. ``Recognition of asphalt pavement crack length using deep convolutional neural networks." Road Materials and Pavement Design 19.6 (2018): 1334-1349.
\bibitem{b38} Sinha, Sunil K., and Paul W. Fieguth. ``Automated detection of cracks in buried concrete pipe images." Automation in construction 15.1 (2006): 58-72.
\bibitem{b39} Nguyen, Hoang-Nam, Tai-Yan Kam, and Pi-Ying Cheng. ``An automatic approach for accurate edge detection of concrete crack utilizing 2D geometric features of crack." Journal of Signal Processing Systems 77 (2014): 221-240.
\bibitem{b40} Kozlov, V. N., A. A. Samokrutov, and V. G. Shevaldykin. ``Thickness measurements and flaw detection in concrete using ultrasonic echo method." Nondestructive Testing and Evaluation 13.2 (1997): 73-84.
\bibitem{b41} Zhou, Huixing, et al. ``A Review of Vision-Laser-Based Civil Infrastructure Inspection and Monitoring." Sensors 22.15 (2022): 5882.
\bibitem{b42} Suzuki, Tetsuya, et al. ``Use of acoustic emission and X-ray computed tomography for damage evaluation of freeze-thawed concrete." Construction and Building Materials 24.12 (2010): 2347-2352.
\bibitem{b43} Daniel Hernández-Contreras, Hayde Peregrina-Barreto, Jose Rangel-Magdaleno, Francisco Renero-Carrillo, ``Plantar Thermogram Database for the Study of Diabetic Foot Complications", IEEE Dataport, October 31, 2019.
\bibitem{b44} Singh, Jaspreet, and Ajat Shatru Arora. ``A framework for enhancing the thermographic evaluation on characteristic areas for paranasal sinusitis detection." Infrared Physics \& Technology 85 (2017): 457-464.
\bibitem{b45} Nguyen, Hung, et al. ``A thermal facial emotion database and its analysis." Pacific-Rim Symposium on Image and Video Technology. Springer, Berlin, Heidelberg, 2013.
\bibitem{b46} M. Kopaczka, R. Kolk and D. Merhof, ``A fully annotated thermal face database and its application for thermal facial expression recognition," 2018 IEEE International Instrumentation and Measurement Technology Conference (I2MTC), 2018, pp. 1-6.
\bibitem{b47} Noble, William S. ``What is a support vector machine?." Nature biotechnology 24.12 (2006): 1565-1567.
\bibitem{b48} Franc, Vojtech, and Václav Hlavác. ``Multi-class support vector machine." 2002 International Conference on Pattern Recognition. Vol. 2. IEEE, 2002.
\bibitem{b49} Suthaharan, Shan, and Shan Suthaharan. ``Support vector machine." Machine learning models and algorithms for big data classification: thinking with examples for effective learning (2016): 207-235.
\bibitem{b50} Blanco, Victor, Justo Puerto, and Antonio M. Rodriguez-Chia. ``On lp-support vector machines and multidimensional kernels." The Journal of Machine Learning Research 21.1 (2020): 469-497.
\bibitem{b51} Peterson, Leif E. ``K-nearest neighbor." Scholarpedia 4.2 (2009): 1883.
\bibitem{b52} Kramer, Oliver, and Oliver Kramer. ``K-nearest neighbors, Dimensionality reduction with unsupervised nearest neighbors", Intelligent Systems Reference Library, volume 51,(2013): 13-23.
\bibitem{b53} Bezdek, James C., Siew K. Chuah, and David Leep. ``Generalized k-nearest neighbor rules." Fuzzy Sets and Systems 18.3 (1986): 237-256.
\bibitem{b54} Gu, Jiuxiang, et al. ``Recent advances in convolutional neural networks." Pattern recognition 77 (2018): 354-377.
\bibitem{b55} O'Shea, Keiron, and Ryan Nash. ``An introduction to convolutional neural networks." arXiv preprint arXiv:1511.08458 (2015).
\bibitem{b56} Albawi, Saad, Tareq Abed Mohammed, and Saad Al-Zawi. ``Understanding of a convolutional neural network." 2017 international conference on engineering and technology (ICET). IEEE, 2017.
\bibitem{b57} Alom, Md Zahangir, et al. ``The history began from alexnet: A comprehensive survey on deep learning approaches." arXiv preprint arXiv:1803.01164 (2018).
\bibitem{b58} Targ, Sasha, Diogo Almeida, and Kevin Lyman. ``Resnet in resnet: Generalizing residual architectures." arXiv preprint arXiv:1603.08029 (2016).
\bibitem{b59} Szegedy, Christian, et al. ``Going deeper with convolutions." Proceedings of the IEEE conference on computer vision and pattern recognition. 2015.
\bibitem{b60} Kennedy, James, and Russell Eberhart. ``Particle swarm optimization." Proceedings of ICNN'95-international conference on neural networks. Vol. 4. IEEE, 1995.
\bibitem{b61} Mirjalili, Seyedali, and Seyedali Mirjalili. ``Genetic algorithm." Evolutionary Algorithms and Neural Networks: Theory and Applications (2019): 43-55.
\bibitem{b62} Ruta, Dymitr, and Bogdan Gabrys. ``An overview of classifier fusion methods." Computing and Information systems 7.1, 2000, pp. 1-10.
\end{thebibliography}